A free/open-source Kazakh-Tatar machine translation system

### 2013-02-27 paper/paper.tex
some more
humble myself and put my name at the end

\name{Ilnar Salimzyanov, Jonathan North Washington, and Francis M. Tyers}

\address{ Kazan Federal University, Indiana University, Universitat d'Alacant \\
          Kazan, Bloomington, Alacant\\
          Russia, IN 47405 (USA), E-03071 Spain\\
          \email{ilnar.salimzyan@gmail.com}, \email{jonwashi@indiana.edu}, \email{ftyers@dlsi.ua.es} \\
}

@@

>>>>

\name{Jonathan North Washington, Francis M. Tyers and Ilnar Salimzyanov}

\address{ Indiana University, Universitat d'Alacant, Kazan Federal University \\
          Bloomington, Alacant, Kazan\\
          IN 47405 (USA), E-03071 Spain, Russia\\
          \email{jonwashi@indiana.edu}, \email{ftyers@dlsi.ua.es},  \email{ilnar.salimzyan@gmail.com} \\
}

@@

%maybe this should be moved to 'Future plans'
Inside the Apertium project, work on several Turkic languages started to be
carried out, with the ultimate goal of creating independent but compatible
finite-state transducers for each language.
%% The idea is that we started Kazakh-Tatar pair to be able to take into account
%% characteristics of two more distant Turkic languages, avoiding narrowing
%% ourselves to mutually intellegible Tatar and Bashkir, but generate
%% transducers which are still compatible and very coherent. Bashkir part of the
%% pair will be updated to the latest developments of Tatar transducer, which
%% took place while working on Kazakh-Tatar.
